\cvsection{Projects}
\begin{cventries}
  \cventry
  {PGTA recruitment system  | React\acvHeaderIconSep\bullet\acvHeaderIconSep Node.js\acvHeaderIconSep\bullet\acvHeaderIconSep MySQL\acvHeaderIconSep\bullet\acvHeaderIconSep GraphQL | \href{https://ta.cs.ucl.ac.uk}{\faHome\acvHeaderIconSep PGTA System}}
  {UCL Department of Computer Science}
  {London, United Kingdom}
  {Jun. 2022 - Present}
  {
    \begin{cvitems}
      \item {Designed and implemented a full-stack web application for managing postgraduate teaching assistant(TA) recruitment.}
      \item {System used by all professors in UCL Computer Science and more than 300 TAs, helps to improve the recruitment process and speed.}
      \item {Designed system prototype to meet the demand of client}
      \item {Designed Database model and GraphQL schema to develop comprehensive backend API}
      \item {Implemented an event-driven microservice infrastructure}
    \end{cvitems}
  }

  \cventry
  {Startup Team Project | Node.js\acvHeaderIconSep\bullet\acvHeaderIconSep Nest.js}
  {CommnRoom co., ltd}
  {UCL BaseKX, United Kingdom}
  {May. 2022 - Sep. 2022}
  {
    \begin{cvitems}
      \item {Work as a full-stack lead software engineer supporting Node.js backend for UCL-sponsored startup.}
      \item {Designed and implemented a Node.js restful backend API using Nest.js framework.}
      \item {Lead the team to migrate backend tech stack from PHP Larval to Node.js.}
      \item {Built and deployed overall service infrastructure utilizing Docker container, CircleCI, and amazon ECS, focusing on high availability and auto-scaling.}
    \end{cvitems}
  }

  \cventry
    {Logic Teaching Software Project | PyQt5\acvHeaderIconSep\bullet\acvHeaderIconSep Python | \href{https://github.com/jerryyangboyu/LogicShark}{\faGithubSquare\acvHeaderIconSep LogicShark Software}}
    {UCL Department of Computer Science} % Organization/group
    {London, United Kingdom} % Location
    {Feb. 2022 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Act as team leader, meet with team members to discuss the software features and write software design proposals}
        \item {Responsible for core graphic module of the overall project, helping other teammates to debug software and learn.}
      \end{cvitems}
    }

  \cventry
    {Open Resource Team Project | Java | \href{https://github.com/jerryyangboyu/dongxin-test-framework}{\faGithubSquare\acvHeaderIconSep DongXin Test Framework}}
    {Beijing Zhizhangyi Technology co., ltd}
    {Beijing, China}
    {Jun. 2021 - Sep. 2021}
    {
      \begin{cvitems}
        \item {Gained expertise in unit testing areas, especially targeted web applications and software.}
        \item {Participated in heavy teamwork on an open-resource project.}
        \item {The testing framework saves the testing team more than 15 percent of the time}
      \end{cvitems}
    }
\end{cventries}
